Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
pass

As it is the case for most empirical evaluations, our findings are
subject to internal, external, and construct validity
threats. Considering internal validity, conceptually, it is possible
that the authors of this paper made mistakes in the implementation of
the scripts supporting the experiments. To mitigate this threat, we
carefully inspected the implementation and results, looking for
inconsistencies whenever possible. As for external validity, our
results might not generalize to other test inputs and engines. To
mitigate this threat, we carefully selected inputs from various
sources according to a well-defined criteria. Likewise, we selected
the engines by using using a well-defined criteria and found that the
engines selected were associated, certainly not by coincidence, with
the browsers informally considered the most popular in the market.
\Fix{One reader might argue that since we mined files from other JS engines,
such as Duktape, JerryScript, JSI, and Tiny-js, we could also run test
transplantation on them. We did not run test transplantation on these
JS engines due to several reasons, including: JSI was deprecated,
TinyJS is not actively maintained. Finally, at the time we started this work,
Duktape and JerryScript did not provide support to ES6. We checked this
information again in Jun 2020, and they are still only partially supporting ES6.
}
In
terms of construct validity, we used standard metrics to determine the
effectiveness of the testing techniques we studied (\eg{}, number of
bugs confirmed and fixed and severity). Engine developers were
responsible for determining the labels of the bug reports and their
severity. Consequently, these metrics originate from a trusted source.

>>>>

As it is the case of most empirical evaluations, our findings are
subject to internal, external, and construct threats to
validity. Considering internal validity, conceptually, it is possible
that the authors of this paper made mistakes in the implementation of
the scripts supporting the experiments. To mitigate this threat, we
carefully inspected the implementation and results, looking for
inconsistencies whenever possible. As for external validity, our
results might not generalize to other test inputs and engines. To
mitigate this threat, we carefully selected inputs from various
sources according to a well-defined criteria. Likewise, we selected
the engines by using using a documented criteria and found that the
engines selected were associated, certainly not by coincidence, with
the browsers informally considered the most popular in the market.  A
reader might argue that since we mined files from other JS engines,
such as Duktape, JerryScript, JSI, and Tiny-js, we could also have ran
test transplantation on them. We decided not to do so for different
reasons: JSI was deprecated, TinyJS is not actively
maintained. Finally, at the time we started this work, Duktape and
JerryScript did not provide support to ES6. We checked this
information again in Jun 2020, and they are still only partially
supporting ES6. In terms of construct validity, we used standard
metrics to determine the effectiveness of the testing techniques we
studied (\eg{}, number of bugs confirmed and fixed and
severity). Engine developers were responsible for determining the
labels of the bug reports and their severity. Consequently, these
metrics originate from a trusted source.
